Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2022-03-04 Methods-and-Results.Rmd
Update Methods-and-Results.Rmd

### Parametric Meta-Analysis
    meta.parametric <- list()
    meta.parametric.sum <- data.frame(effect = var, 
                                      name = names, 
                                      beta.Worker = NA, 
                                      CI.Worker = NA,
                                      beta.Student = NA, 
                                      CI.Student = NA,
                                      beta.Medical = NA,
                                      CI.Medical = NA, 
                                      RE.beta = NA,
                                      RE.CI = NA,
                                      RE.pval = NA,
                                      RE.star = NA)

@@

      meta.parametric.sum$effect[i] <- var[i]
      meta.parametric.sum$beta.Worker[i] <- meta.parametric[[var[i]]]$yi[1]
      meta.parametric.sum$beta.Student[i] <- meta.parametric[[var[i]]]$yi[2]
      meta.parametric.sum$beta.Medical[i] <- meta.parametric[[var[i]]]$yi[3]
      meta.parametric.sum$CI.Worker[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[1]-1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2),", ",round(meta.parametric[[var[i]]]$yi[1]+1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2),"]",sep="")
      meta.parametric.sum$CI.Student[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[2]-1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2),", ",round(meta.parametric[[var[i]]]$yi[2]+1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2),"]",sep="")
      meta.parametric.sum$CI.Medical[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[3]-1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2),", ",round(meta.parametric[[var[i]]]$yi[3]+1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2),"]",sep="")
      meta.parametric.sum$RE.beta[i] <- meta.parametric[[var[i]]]$b
      meta.parametric.sum$RE.CI[i] <- paste("[",
                                            round(meta.parametric[[var[i]]]$ci.lb, 2),
                                            ", ", round(meta.parametric[[var[i]]]$ci.ub,2),"]", sep="")
      meta.parametric.sum$RE.pval[i] <- meta.parametric[[var[i]]]$pval
      meta.parametric.sum$RE.star[i] <- ifelse(meta.parametric.sum$RE.pval[i]<0.001,"***",ifelse(meta.parametric.sum$RE.pval[i]<0.01,"**",ifelse(meta.parametric.sum$RE.pval[i]<0.05,"*","")))
}
    #meta.parametric

@@

>>>>

### Parametric Meta-Analysis
    meta.parametric <- list()
    meta.parametric.sum <- data.frame(effect = var, 
                                      name = names, 
                                      beta.Worker = NA, 
                                      lwr.Worker = NA, 
                                      upr.Worker = NA, 
                                      CI.Worker = NA,
                                      beta.Student = NA, 
                                      lwr.Student = NA, 
                                      upr.Student = NA, 
                                      CI.Student = NA,
                                      beta.Medical = NA,
                                      lwr.Medical = NA,
                                      upr.Medical = NA,
                                      CI.Medical = NA, 
                                      RE.beta = NA,
                                      lwr.RE = NA,
                                      upr.RE = NA,
                                      RE.CI = NA,
                                      RE.pval = NA,
                                      RE.star = NA)

@@

      meta.parametric.sum$effect[i] <- var[i]
      meta.parametric.sum$beta.Worker[i] <- meta.parametric[[var[i]]]$yi[1]
      meta.parametric.sum$beta.Student[i] <- meta.parametric[[var[i]]]$yi[2]
      meta.parametric.sum$beta.Medical[i] <- meta.parametric[[var[i]]]$yi[3]

      meta.parametric.sum$lwr.Worker[i] <- meta.parametric[[var[i]]]$yi[1]-1.96*sqrt(meta.parametric[[var[i]]]$vi[1])
      meta.parametric.sum$lwr.Student[i] <- meta.parametric[[var[i]]]$yi[2]-1.96*sqrt(meta.parametric[[var[i]]]$vi[2])
      meta.parametric.sum$lwr.Medical[i] <- meta.parametric[[var[i]]]$yi[3]-1.96*sqrt(meta.parametric[[var[i]]]$vi[3])

      meta.parametric.sum$upr.Worker[i] <- meta.parametric[[var[i]]]$yi[1]+1.96*sqrt(meta.parametric[[var[i]]]$vi[1])
      meta.parametric.sum$upr.Student[i] <- meta.parametric[[var[i]]]$yi[2]+1.96*sqrt(meta.parametric[[var[i]]]$vi[2])
      meta.parametric.sum$upr.Medical[i] <- meta.parametric[[var[i]]]$yi[3]+1.96*sqrt(meta.parametric[[var[i]]]$vi[3])

      meta.parametric.sum$CI.Worker[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[1]-1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2),", ",round(meta.parametric[[var[i]]]$yi[1]+1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2),"]",sep="")
      meta.parametric.sum$CI.Student[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[2]-1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2),", ",round(meta.parametric[[var[i]]]$yi[2]+1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2),"]",sep="")
      meta.parametric.sum$CI.Medical[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[3]-1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2),", ",round(meta.parametric[[var[i]]]$yi[3]+1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2),"]",sep="")

      meta.parametric.sum$RE.beta[i] <- meta.parametric[[var[i]]]$b
      meta.parametric.sum$lwr.RE[i] <- meta.parametric[[var[i]]]$ci.lb
      meta.parametric.sum$upr.RE[i] <- meta.parametric[[var[i]]]$ci.ub
      meta.parametric.sum$RE.CI[i] <- paste("[",
                                            round(meta.parametric[[var[i]]]$ci.lb, 2),
                                            ", ", round(meta.parametric[[var[i]]]$ci.ub,2),"]", sep="")
      meta.parametric.sum$RE.pval[i] <- meta.parametric[[var[i]]]$pval
      meta.parametric.sum$RE.star[i] <- ifelse(meta.parametric.sum$RE.pval[i]<0.001,"***",ifelse(meta.parametric.sum$RE.pval[i]<0.01,"**",ifelse(meta.parametric.sum$RE.pval[i]<0.05,"*","")))

}
    #meta.parametric

    meta.parametric.plt.data <- meta.parametric.sum

    meta.parametric.sum <- meta.parametric.sum %>%
      select(-starts_with("lwr"),
             -starts_with("upr"))

@@

    meta.parametric.plt.data <- data.table(meta.parametric.plt.data) %>% 
        mutate(
          beta.RE = RE.beta,
          CI.RE = RE.CI,
          pval.RE = RE.pval,
          star.RE = RE.star
        ) %>%
      select(-starts_with("RE."))

    meta.parametric.plt.widedata <- data.table::melt.data.table(
      data = meta.parametric.plt.data,
      id.vars = c("effect", "name"),
      measure.vars = patterns(
        beta = "beta",
        lwr = "lwr",
        upr = "upr",
        CI = "CI",
        pval = "pval",
        star = "star"
      ),
      variable = "sample" # sample info missing
    )
